A recipe for highly reproducible enrichment analysis (and why we need it)

### 2024-03-01 manuscript/manuscript.Rmd
ms work

The lists of genes were collected from the supplementary files and stored in a spreadsheet, paying
special attention to preventing gene name errors from occurring @Zeeberg2004-na.
The reproducibility analysis was performed using the respective methodologies stated in the methods
sections of the 20 articles using the DAVID version specified in the articles (March-May 2022) [@Sherman2022-hf].

@@

Although this reproducibility study is relatively small, there are a few key observations.
We observe that only 4/20(20%) of studies achieved a high degree of reproducibility.
In a way, this is unexpected, given the simplicity of using DAVID.
Users provide a list of gene identifiers in a text box and select some options.
There are several possible explanations for this inconsistency:

>>>>

The lists of genes were collected from the supplementary files and stored in a spreadsheet, paying
special attention to preventing gene name errors from occurring @Zeeberg2004-na.
The reproducibility analysis was performed using the respective methodologies stated in the methods
sections of the 20 articles using DAVID version 6.8 (conducted March-May 2022) [@Sherman2022-hf].

@@

There are some notable limitations of this reproduction work.
The sample size of 20 is relatively small.
The articles were selected randomly from a list of articles that cited DAVID, and they are mostly from
low and mid-tier journals (mean SJR 2022: 1.2, SD=0.68) and the results may not be representative of
higher-tier journal articles.
This is not a complete reproduction of all work in those papers; we only reproduced the DAVID functional enrichment analysis,
which typically is just one component of an article that can have several other parts, including
experimental validation of key findings.
Therefore, if we identified that the enrichment analysis was not reproducible, it does not automatically mean that
all results and conclusions are flawed.

Despite these limitations, there are a few key observations.
We observe that only 4/20(20%) of studies achieved a high degree of reproducibility.
In a way, this is unexpected, given the simplicity of using DAVID.
Users provide a list of gene identifiers in a text box and select some options.
There are several possible explanations for this inconsistency:
